---
title: "CCCEH Survey Analysis"
author: "Eleanor Medley and Kendall Kruchten"
date: "7/19/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(readr)
library(tidyverse)
library(dplyr)
library(tidyr) #For splitting comma
library(labelled)
library(naniar) #Allows us to replace all missing values with NA
library(data.table) #For splitting comma
```

## Import Data
```{r, import}
# import first data set
practice_data <- read.csv("Responses3.csv")
#view(practice_data)

# ESTABLISH CODEBOOK!

# get rid of first row of observations (the questions)
practice_data <- practice_data[-1,]
#view(practice_data)

# add a column that indicates the source
practice_data <- practice_data %>% mutate(data_source = "YMCA")
# glimpse(practice_data)

# import next data set (for now, I'll just re-import the same one)
practice_data2 <- read.csv("Responses3.csv")
#view(practice_data2)

# get rid of first row of observations (the questions)
practice_data2 <- practice_data2[-1,]
#view(practice_data2)

# add a column that indicates the source (different from the first data set)
practice_data2 <- practice_data2 %>% mutate(data_source = "Scouts")
# glimpse(practice_data2)

# Merge the data sets
all_practice_data <- rbind(practice_data, practice_data2)
#view(all_practice_data)

# NOTE: numbers on the far left are automatically assigned by R and are weird. Add an ID column with ID numbers assigned to respondents sequentially. 
all_practice_data <- all_practice_data %>% mutate(ID = 1:n()) %>% select(ID, everything())

```

###Change Missing to NA
```{r, missing}
missing_values <- c("")
all_practice_data <- all_practice_data %>%
  replace_with_na_if(.predicate = is.character,
                     condition = ~.x %in% (missing_values))
# view(all_practice_data)

#Below only worked for questions that return a number: 
#all_practice_data2 %>%
#  replace_with_na_all(condition = ~.x %in% missing_values)
#view(all_practice_data2)
```

##Split Answer Choice where comma occurs
```{r, split}
#These two methods don't really do what we want them to do. It will split into new rows the different races for parents and children. So for child 1, when you do this by child and parent race it creates 8 responses.
practice <- all_practice_data
practice2 <- practice %>% 
  mutate(practice = strsplit(as.character(Q6), ",")) %>%
  unnest(practice)
view(practice2)

practice3 <- separate_rows(all_practice_data, Q6, sep = ",", convert = TRUE)
practice3 <- separate_rows(all_practice_data, X1_Q14, sep = ",", convert = TRUE)
practice3 <- separate_rows(all_practice_data, X2_Q14, sep = ",", convert = TRUE)
practice3 <- separate_rows(all_practice_data, X3_Q14, sep = ",", convert = TRUE)
practice3 <- separate_rows(all_practice_data, X4_Q14, sep = ",", convert = TRUE)
practice3 <- separate_rows(all_practice_data, X5_Q14, sep = ",", convert = TRUE)
view(practice3)

# So we could do it like this...but it would be A LOT 

all_practice_data_test <- all_practice_data %>%
  transform(X1_Q14_native = grepl("American Indian or Alaska Native", X1_Q14),
            X1_Q14_black = grepl("Black or African American", X1_Q14),
            X1_Q14_eastasian = grepl("East Asian", X1_Q14),
            X1_Q14_latinx = grepl("Hispanic / Latinx", X1_Q14),
            X1_Q14_mena = grepl("Middle Eastern or North African", X1_Q14),
            X1_Q14_hawaii = grepl("Native Hawaiian or Pacific Islander", X1_Q14),
            X1_Q14_southasian = grepl("South Asian", X1_Q14),
            X1_Q14_white = grepl("White", X1_Q14),
            X1_Q14_none = grepl("Prefer not to answer", X1_Q14))

# https://community.rstudio.com/t/a-use-case-for-tidyr-chop-check-all-that-apply-survey-questions/47859/2 
```

```{r, all that apply, eval = FALSE}
## template for analyzing Select All That Apply questions (code written by Miranda)
##turns comma separated responses into dummy variables with the response as the column name (ie, “23.skin”, “23.hair”)
dat <- strsplit(samp$X1_Q23, ",")
lvls <- unique(unlist(dat))
kid1 <- structure(lapply(lvls, function(lvl) sapply(dat, function(xx) lvl %in% xx)),
                 .Names = paste0('Q23.', lvls),
                 row.names = c(NA, -length(dat)), class = 'data.frame')
kid1 <- 1 * kid1 ## convert from TRUE/FALSE to 1/0
 
dat <- strsplit(samp$X2_Q23, ",")
lvls <- unique(unlist(dat))
kid2 <- structure(lapply(lvls, function(lvl) sapply(dat, function(xx) lvl %in% xx)),
                 .Names = paste0('Q23.', lvls),
                 row.names = c(NA, -length(dat)), class = 'data.frame')
kid2 <- 1 * kid2
 
dat <- strsplit(samp$X3_Q23, ",")
lvls <- unique(unlist(dat))
kid3 <- structure(lapply(lvls, function(lvl) sapply(dat, function(xx) lvl %in% xx)),
                  .Names = paste0('Q23.', lvls),
                  row.names = c(NA, -length(dat)), class = 'data.frame')
kid3 <- 1 * kid3
 
dat <- strsplit(samp$X4_Q23, ",")
lvls <- unique(unlist(dat))
kid4 <- structure(lapply(lvls, function(lvl) sapply(dat, function(xx) lvl %in% xx)),
                  .Names = paste0('Q23.', lvls),
                  row.names = c(NA, -length(dat)), class = 'data.frame')
kid4 <- 1 * kid4
 
dat <- strsplit(samp$X5_Q23, ",")
lvls <- unique(unlist(dat))
kid5 <- structure(lapply(lvls, function(lvl) sapply(dat, function(xx) lvl %in% xx)),
                  .Names = paste0('Q23.', lvls),
                  row.names = c(NA, -length(dat)), class = 'data.frame')
kid5 <- 1 * kid5
 
q23 <- dplyr::bind_rows(kid1, kid2, kid3, kid4, kid5)
 
##creates the table of frequencies and counts
adply(q23[grepl("Q23.", colnames(q23))], 2, function(x)
  data.frame(Count = as.data.frame(table(x))[2,2],
             Perc = as.data.frame(prop.table(table(x)))[2,2]))
```

##Child Age Demographics
```{r, age}
# Start by adding a new variable of child age groups:
# 0 - 3 (Infants)
# 4 - 6 (Preschool and Kindergarten)
# 7 - 9 (Early Elementary)
# 10 - 12 (Late Elementary/Early Middle School)

# Convert child ages to numbers
child_age <- c("X1_Q12", "X2_Q12", "X3_Q12", "X4_Q12", "X5_Q12")
all_practice_data[child_age] <- sapply(all_practice_data[child_age], as.numeric)
glimpse(all_practice_data)

# Add age category variable
all_practice_data <- all_practice_data %>% 
  mutate(X1_age_cat = if_else(X1_Q12 <= 3, "0-3", 
                            if_else(X1_Q12 <= 6, "4-6", 
                            if_else(X1_Q12 <= 9, "7-9",
                            if_else(X1_Q12 <= 12, "10-12", NA_character_)))))

all_practice_data <- all_practice_data %>% 
  mutate(X2_age_cat = if_else(X2_Q12 <= 3, "0-3", 
                            if_else(X2_Q12 <= 6, "4-6", 
                            if_else(X2_Q12 <= 9, "7-9",
                            if_else(X2_Q12 <= 12, "10-12", NA_character_)))))

all_practice_data <- all_practice_data %>% 
  mutate(X3_age_cat = if_else(X3_Q12 <= 3, "0-3", 
                            if_else(X3_Q12 <= 6, "4-6", 
                            if_else(X3_Q12 <= 9, "7-9",
                            if_else(X3_Q12 <= 12, "10-12", NA_character_)))))

all_practice_data <- all_practice_data %>% 
  mutate(X4_age_cat = if_else(X4_Q12 <= 3, "0-3", 
                            if_else(X4_Q12 <= 6, "4-6", 
                            if_else(X4_Q12 <= 9, "7-9",
                            if_else(X4_Q12 <= 12, "10-12", NA_character_)))))

all_practice_data <- all_practice_data %>% 
  mutate(X5_age_cat = if_else(X5_Q12 <= 3, "0-3", 
                            if_else(X5_Q12 <= 6, "4-6", 
                            if_else(X5_Q12 <= 9, "7-9",
                            if_else(X5_Q12 <= 12, "10-12", NA_character_)))))

# make subdataset Q12 with child ages and age groups
Q12 <- all_practice_data %>% select(ID, X1_Q12, X2_Q12, X3_Q12, X4_Q12, X5_Q12)
Q12 <- Q12 %>% pivot_longer(!ID, names_to = "child", values_to = "child_age")

Q12_2 <- all_practice_data %>% select(ID, X1_age_cat, X2_age_cat, X3_age_cat, X4_age_cat, X5_age_cat)
Q12_2 <- Q12_2 %>% pivot_longer(!ID, names_to = "child", values_to = "child_age_cat")

Q12 <- Q12_2 %>% select(child_age_cat) %>% cbind(Q12) %>% select(ID, child, child_age, child_age_cat)

# Proportions for each individual age
Q12 %>% drop_na() %>% count(child_age) %>% mutate(prop = n/sum(n))

#    Age     n   prop
#  <dbl> <int>  <dbl>
#1     0     2 0.0667
#2     1     6 0.2   
#3     2     2 0.0667
#4     5     4 0.133 
#5     6     4 0.133 
#6     8     2 0.0667
#7    10     2 0.0667
#8    11     2 0.0667
#9    12     6 0.2  

# Proportions for each age category 
Q12 %>% 
  drop_na() %>% 
  count(child_age_cat) %>% 
  mutate(prop = n/sum(n)) 

#  AgeCat   n    prop
#  <chr>  <int>  <dbl>
# 0-3       10	0.33333333		
# 10-12	    10	0.33333333		
# 4-6     	8	  0.26666667		
# 7-9	      2	  0.06666667	
```

## Child Gender Demographics
```{r, gender}
# Q13 What gender identity best describes Child X?

Q13 <- all_practice_data %>% select(ID, X1_Q13, X2_Q13, X3_Q13, X4_Q13, X5_Q13)
#view(Q13)
Q13 <- Q13 %>% pivot_longer(!ID, names_to = "child", values_to = "child_gender")
#view(Q13)

Q13 %>% drop_na() %>%
  count(child_gender) %>%
  mutate(prop = n/sum(n))

#Results
#gender n   prop
#Female	18	0.6		
#Male	  12	0.4	
```

## Child Race/Ethnicity Demographics
```{r}
# Q14 What race/ethnicity category best describes Child X? (If your child is two or more races/ethnicities, please select all that apply)
# Thinking about above when we want to analyze do we want to have their race reflect multi and bi-racial? I think it is important it just may give us a lot of results and lessen the strength of our analysis 

Q14 <- all_practice_data %>% select(ID, X1_Q14, X2_Q14, X3_Q14, X4_Q14, X5_Q14)
Q14 <- Q14 %>% pivot_longer(!ID, names_to = "child", values_to = "child_race_eth")

Q14 %>% drop_na() %>%
  count(child_race_eth) %>%
  mutate(prop = n/sum(n))

#Results
#race_eth                         n   prop
#American Indian or Alaska Native 2	  0.06666667		
#Black or African American	      6	  0.20000000		
#Black or African American,White	16	0.53333333		
#East Asian	                      6	  0.20000000	
```

# Parent Demographics 
```{r}
# Parent Race/ethnicity
Q6 <- all_practice_data %>% select(ID, Q6) %>% rename(parent_race_eth = Q6)

Q6 %>% drop_na() %>%
  count(parent_race_eth) %>%
  mutate(prop = n/sum(n))

#Results
#parent_race_eth                  n   prop
#American Indian or Alaska Native	2	0.2		
#Black or African American	      2	0.2		
#Black or African American,White	4	0.4		
#East Asian	                      2	0.2	


# Household income
Q8 <- all_practice_data %>% select(ID, Q8) %>% rename(income = Q8)

#Parent Education
Q7 <- all_practice_data %>% select(ID, Q7) %>% rename(education = Q7)

```

## Direct Motivation: Play vs. Beautification Rating 
```{r, rating}
# For each child 12 and under, rate on a scale of 1-10 how much they wear children's makeup and body products as play versus for beautification?

# First, need to convert ratings from chr to number
ratings <- c("X1_Q31_1", "X2_Q31_1", "X3_Q31_1", "X4_Q31_1", "X5_Q31_1")
all_practice_data[ratings] <- sapply(all_practice_data[ratings], as.numeric)
glimpse(all_practice_data)

# Create a sub dataset that is just the rating questions
Q31 <- all_practice_data %>% select(ID, X1_Q31_1, X2_Q31_1, X3_Q31_1, X4_Q31_1, X5_Q31_1)
Q31 <- Q31 %>% pivot_longer(!ID, names_to = "child", values_to = "rating")
view(Q31)
Q31 %>% filter(!is.na(rating)) %>% summarise(mean = mean(rating))
summary(Q31$rating)
# Summary above gives you overall mean 

# Mean rating by child age group
Q31_demo <- Q12 %>% select(child_age_cat) %>% cbind(Q31) %>% select(ID, child, rating, child_age_cat)
Q31_demo %>% drop_na() %>%
  group_by(fct_relevel(child_age_cat, "0-3", "4-6", "10-12")) %>%
  summarise(mean_rating = mean(rating))

#We will have to add 7-9 when we get results for that age group. 
#Results
#Age Cat  Score
#0-3	    9.333333
#4-6	    6.250000
#10-12	  2.200000

# Mean rating by child gender
Q31_demo <- Q13 %>% select(child_gender) %>% cbind(Q31_demo) %>% select(ID, child, rating, child_age_cat, child_gender)
Q31_demo %>% drop_na() %>%
  group_by(child_gender) %>%
  summarise(mean_rating = mean(rating))

#Results
#gender #mean_rating
#Female	6.5			
#Male	  3.0	

# Mean rating by child race/ethnicity
Q31_demo <- Q14 %>% select(child_race_eth) %>% cbind(Q31_demo) %>% select(ID, child, rating, child_age_cat, child_gender, child_race_eth)
Q31_demo %>% drop_na() %>%
  group_by(child_race_eth) %>%
  summarise(mean_rating = mean(rating))

#Results
#child_race_eth                   mean_rating
#American Indian or Alaska Native	8.000000		
#Black or African American,White	4.625000		
#East Asian	                      6.333333	

#Rating by Parent Income
Q31_demo <- Q8 %>% select(income) %>% cbind(Q31_demo) %>% select(ID, child, rating, income)

Q31_demo %>% drop_na() %>%
  group_by(fct_relevel(income, "$25k - $75k", "$75k - $125k", "$125k - $175k", "$175k+", "Prefer not to answer")) %>%
  summarise(mean_rating = mean(rating))
#Results 
#$25k - $75k	          5.000000		
#$75k - $125k	          3.500000		
#$125k - $175k	        5.500000		
#$175k+	                8.666667		
#Prefer not to answer	  4.000000
#those with higher incomes tend to use products more in beautification than play. 
```

## Indirect Motivation: Duration of use
```{r, duration}
# Q26 In the last year, approximately how long does this child wear children's makeup and body products for when they use them? 
# 0-2 hours, 2-4 hours, 4-6 hours, 6-8 hours, 8+ hours, Do not know

# Combine data from all children into 1 table and assess distribution overall
Q26 <- all_practice_data %>% select(ID, X1_Q26, X2_Q26, X3_Q26, X4_Q26, X5_Q26)
Q26 <- Q26 %>% pivot_longer(!ID, names_to = "child", values_to = "duration")
#view(Q26)

Q26 %>% filter(!is.na(duration)) %>% count(duration) %>% mutate(prop = n/sum(n))

# Results
#duration   n   prop
#0-2 hours  8	  0.33333333		
#2-4 hours	14  0.58333333		
#8+ hours	  2	  0.08333333	

# Duration of use by child age category 
Q26_demo <- Q12 %>% select(child_age_cat) %>% cbind(Q26) %>% select(ID, child, duration, child_age_cat)
# view(Q26_Q12)

Q26_demo %>%
  drop_na() %>%
  group_by(child_age_cat) %>%
  count(duration) %>%
  mutate(prop = n/sum(n))

# Results 
# Age   Duration    n prop
# 0-3	  0-2 hours	  4	0.6666667	
# 0-3	  8+ hours	  2	0.3333333	
# 10-12	0-2 hours	  2	0.2000000	
# 10-12	2-4 hours	  8	0.8000000	
# 4-6	  0-2 hours	  2	0.2500000	
# 4-6	  2-4 hours	  6	0.7500000

# Duration of use by child gender
Q26_demo <- Q13 %>% select(child_gender) %>% cbind(Q26_demo) %>% select(ID, child, duration, child_age_cat, child_gender)
#view(Q26_Q13)

Q26_demo %>%
  drop_na() %>%
  group_by(child_gender) %>%
  count(duration) %>%
  mutate(prop = n/sum(n))

#Results
#Gender Duration  n   prop
#Female	0-2 hours	4	  0.250	
#Female	2-4 hours	10	0.625	
#Female	8+ hours	2	  0.125	
#Male	0-2 hours	  4	  0.500	
#Male	2-4 hours	  4	  0.500	

# Duration of use by child race/ethnicity
Q26_demo <- Q14 %>% select(child_race_eth) %>% cbind(Q26_demo) %>% select(ID, child, duration, child_age_cat, child_gender, child_race_eth)
#view(Q26_Q14)

Q26_demo %>% 
  drop_na() %>% 
  group_by(child_race_eth) %>%
  count(duration) %>%
  mutate(prop = n/sum(n))

#Results
#race_eth                         duration  n   prop
#American Indian or Alaska Native	0-2 hours	2	  1.0000000	
#Black or African American,White	0-2 hours	4	  0.2500000	
#Black or African American,White	2-4 hours	12	0.7500000	
#East Asian	                      0-2 hours	2 	0.3333333	
#East Asian	                      2-4 hours	2	  0.3333333	
#East Asian	                      8+ hours	2	  0.3333333	

```

## Indirect Motivation: Wear Outside Home
```{r}
Q30 <- all_practice_data %>% select(ID, X1_Q30, X2_Q30, X3_Q30, X4_Q30, X5_Q30)

Q30 <- Q30 %>% pivot_longer(!ID, names_to = "child", values_to = "outside")
#view(Q30)

Q30 %>% drop_na() %>%
  count(fct_relevel(outside, "Never", "Rarely", "Sometimes", "Often", "Always", "Do not know")) %>%
  mutate(prop = n/sum(n))
#Results    n   %
#Never	    2	  0.08333333		
#Sometimes	6	  0.25000000		
#Often	    10	0.41666667		
#Always	    6	  0.25000000

#By child age category
Q30_demo <- Q12 %>% select(child_age_cat) %>% cbind(Q30) %>% select(ID, child, outside, child_age_cat)
# view(Q30_Q12)

Q30_demo %>%
  drop_na() %>%
  group_by(fct_relevel(child_age_cat, "0-3", "4-6", "7-9", "10-12")) %>%
  count(outside) %>%
  mutate(prop = n/sum(n))

#Results
#0-3    Never	      2	0.3333333
#0-3    Often	      2	0.3333333
#0-3    Sometimes	  2	0.3333333
#4-6    Always	    2	0.2500000
#4-6    Often	      6	0.7500000
#10-12  Always	    4	0.4000000
#10-12  Often	      2	0.2000000
#10-12  Sometimes	  4	0.4000000

#By child gender
Q30_demo <- Q13 %>% select(child_gender) %>% cbind(Q30_demo) %>% select(ID, child, outside, child_age_cat, child_gender)
# view(Q30_gender)

Q30_demo %>%
  drop_na() %>%
  group_by(child_gender) %>%
  count(outside) %>%
  mutate(prop = n/sum(n))

#Results 
#Female	  Always	    2	0.125	
#Female	  Never	      2	0.125	
#Female 	Often	      6	0.375	
#Female	  Sometimes	  6	0.375	
#Male	    Always	    4	0.500	
#Male	    Often	      4	0.500	

#By child race/ethnicity
Q30_demo <- Q14 %>% select(child_race_eth) %>% cbind(Q30_demo) %>% select(ID, child, outside, child_age_cat, child_gender, child_race_eth)

Q30_demo %>%
  drop_na() %>%
  group_by(child_race_eth) %>%
  count(outside) %>%
  mutate(prop = n/sum(n))

#Results 
#American Indian or Alaska Native	Sometimes	2	  1.0
#Black or African American,White	Always	  4	  0.25
#Black or African American,White	Never	    2	  0.125
#Black or African American,White	Often   	6	  0.375
#Black or African American,White	Sometimes	4	  0.25
#East Asian                     	Always  	2	  0.333
#East Asian	                      Often	    4   0.667
```

## Indirect Motivation: Who applies the cosmetics?
```{r, applies}
#Q27, Who applies the children's makeup and body products to Child X? (Select all that apply)

# Overall
Q27 <- all_practice_data %>% select(ID, X1_Q27, X2_Q27, X3_Q27, X4_Q27, X5_Q27)
Q27 <- Q27 %>% pivot_longer(!ID, names_to = "child", values_to = "applies")
#view(Q27)

Q27 %>% drop_na() %>%
  count(applies) %>%
  mutate(prop = n/sum(n))

# Will have to figure out how to analyze these all that apply questions...

# By parent race/ethnicity

Q27_demo <- Q6 %>% select(parent_race_eth) %>% cbind(Q27) %>% select(ID, applies, parent_race_eth)


```

### All Children
```{r}
#Q39 How often do you read the ingredients list before purchasing children's makeup and body products

Q39 <- all_practice_data %>% select(ID, Q39) %>% rename(ingredients = Q39)
Q39 %>% drop_na() %>% count(ingredients) %>% mutate(prop = n/sum(n))

#Results 
#Never	4	0.5		
#Rarely	4	0.5	

#Ingredients by Parent Race 
Q39_demo <- Q6 %>% select(parent_race_eth) %>% cbind(Q39) %>% select(ID, ingredients, parent_race_eth)
# view(Q39_demo)

Q39_demo %>%
  drop_na() %>%
  group_by(parent_race_eth) %>%
  count(ingredients) %>%
  mutate(prop = n/sum(n))

#Results 
#American Indian or Alaska Native	  Rarely	2	1
#Black or African American	        Rarely	2	1
#Black or African American,White	  Never	  4	1

#By education
all_practice_data %>%
  group_by(fct_relevel(Q7, "Less than high school", "High school / Equivalent", "Vocational/trade school", "Some college", "Completed college", "Some graduate school or more", "Prefer not to answer")) %>%
  count(Q39) %>%
  mutate(prop = n/sum(n))

#Results 
#Vocational/trade school	        NA	2	1.0	
#Some college	                    Rarely	2	1.0	
#Completed college	              Never	2	0.5	
#Completed college	              Rarely	2	0.5	
#Some graduate school or more	    Never	2	1.0	

all_practice_data %>%
  group_by(fct_relevel(Q8, "$25k - $75k", "$75k - $125k", "$125k - $175k", "$175k+", "Prefer not to answer")) %>%
  count(Q39) %>%
  mutate(prop = n/sum(n))
#Results               Freq   n %
#$25k - $75k	         NA	    2	1	
#$75k - $125k	         Rarely	4	1	
#$125k - $175k	       Never	2	1	
#$175k+	               Never  2	1	
#Prefer not to answer	 NA	    2	1	

#By Parent Age 
all_practice_data %>%
  group_by(fct_relevel(Q4, "18-24", "25-29", "30-34", "35-39", "40-44", "45-49", "50-54", "55-59", "60+", "Prefer not to answer")) %>%
  count(Q39) %>%
  mutate(prop = n/sum(n))
#Results 
#18-24	Rarely	2	1.0	
#30-34	NA	    2	1.0	
#35-39	Rarely	2	0.5	
#35-39	NA	    2	0.5	
#40-44	Never	  4	1.0	

#Q40 Approximately how frequently do you buy children's makeup and body products for your children 12 and under? 

Q40 <- all_practice_data %>% select(ID, Q40)
Q40 <- Q40 %>% pivot_longer(!ID, names_to = "parent", values_to = "purchase_freq")
Q40 %>% filter(!is.na(purchase_freq)) %>% count(purchase_freq) %>% mutate(prop = n/sum(n))

#             Q40 n prop
#1 Every 6 months 4  0.5
#2    Once a year 4  0.5

#Ingredients by Parent Race 
Q40_demo <- Q6 %>% select(parent_race_eth) %>% cbind(Q40) %>% select(ID, parent, purchase_freq, parent_race_eth)
# view(Q40_demo)

Q40_demo %>%
  drop_na() %>%
  group_by(parent_race_eth) %>%
  count(purchase_freq) %>%
  mutate(prop = n/sum(n))
#             Q40 n prop
#American Indian or Alaska Native	Once a year	    2	1.0
#Black or African American	      Every 6 months	2	1.0
#Black or African American,White	Every 6 months	2	0.5
#Black or African American,White	Once a year	    2	0.5

#freq Purcahse by Education
#By education
all_practice_data %>%
  group_by(fct_relevel(Q7, "Less than high school", "High school / Equivalent", "Vocational/trade school", "Some college", "Completed college", "Some graduate school or more", "Prefer not to answer")) %>%
  count(Q40) %>%
  mutate(prop = n/sum(n))
#Results 
#Vocational/trade school	        NA	            2	1.0
#Some college	                    Every 6 months	2	1.0
#Completed college	              Every 6 months	2	0.5
#Completed college	              Once a year	    2	0.5
#Some graduate school or more	    Once a year	    2	1.0
#NA	                              NA	            2	1.0

#Freq Purchase by Income
all_practice_data %>%
  group_by(fct_relevel(Q8, "$25k - $75k", "$75k - $125k", "$125k - $175k", "$175k+", "Prefer not to answer")) %>%
  count(Q40) %>%
  mutate(prop = n/sum(n))
#Results 
#$25k - $75k	          NA	            2	1.0	
#$75k - $125k	          Every 6 months	2	0.5	
#$75k - $125k	          Once a year	    2	0.5	
#$125k - $175k	        Every 6 months	2	1.0	
#$175k+	                Once a year	    2	1.0	
#Prefer not to answer	  NA	            2	1.0	
```


###Q25
```{r}
# Q25 In the last year, approximately how often does Child 1 use children's makeup and body products? 
# "Once a year or less", "A few times a year", "Monthly", "Once every two weeks", "Weekly", "Daily or more", "do not know"

# Combine data from all children into 1 table and assess distribution overall
Q25 <- all_practice_data %>% select(ID, X1_Q25, X2_Q25, X3_Q25, X4_Q25, X5_Q25)
Q25 <- Q25 %>% pivot_longer(!ID, names_to = "child", values_to = "freq_use")
#view(Q25)

Q25 %>% filter(!is.na(freq_use)) %>% count(fct_relevel(freq_use, "Once a year or less", "A few times a year", "Monthly", "Once every two weeks", "Weekly", "Daily or more", "Do not know")) %>% mutate(prop = n/sum(n))

# Results
#freq use             n   prop
#Once a year or less	  6	0.2500000	
#A few times a year	    10	0.4166667	
#Monthly	              8	0.3333333	

# Freq of use by child age category 
Q25_demo <- Q12 %>% select(child_age_cat) %>% cbind(Q25) %>% select(ID, child, freq_use, child_age_cat)
# view(Q25_demo)

Q25_demo %>%
  drop_na() %>%
  group_by(fct_relevel(child_age_cat, "0-3", "4-6", "10-12")) %>%
  count(freq_use) %>%
  mutate(prop = n/sum(n))

# Results 
# Age   Duration    n prop
#0-3        A few times a year	4	0.6666667
#0-3        Monthly	2	0.3333333
#4-6        A few times a year	2	0.2500000
#4-6        Monthly	2	0.2500000
#4-6        Once a year or less	4	0.5000000
#10-12        A few times a year	4	0.4000000
#10-12        Monthly	4	0.4000000
#10-12        Once a year or less	2	0.2000000


# Duration of use by child gender
Q25_demo <- Q13 %>% select(child_gender) %>% cbind(Q25_demo) %>% select(ID, child, freq_use, child_age_cat, child_gender)
#view(Q25_demo)

Q25_demo %>%
  drop_na() %>%
  group_by(child_gender) %>%
  count(freq_use) %>%
  mutate(prop = n/sum(n))

#Results
#Gender Duration  n   prop
#Female	A few times a year	  6	0.375	
#Female	Monthly	              8	0.500	
#Female	Once a year or less	  2	0.125	
#Male	A few times a year	    4	0.500	
#Male	Once a year or less	    4	0.500		

# Duration of use by child race/ethnicity
Q25_demo <- Q14 %>% select(child_race_eth) %>% cbind(Q25_demo) %>% select(ID, child, freq_use, child_age_cat, child_gender, child_race_eth)
#view(Q25_demo)

Q25_demo %>% 
  drop_na() %>% 
  group_by(child_race_eth) %>%
  count(freq_use) %>%
  mutate(prop = n/sum(n))

#Results
#race_eth         freq  n   prop
#American Indian	A few times a year	2	1.0000000
#Blak, White      A few times a year	8	0.5000000
#Black, White     Monthly	            6	0.3750000
#Black, White     Once a year or less	2	0.1250000
#East ASian       Monthly	            2	0.3333333
#East ASian       Once a year or less	4	0.6666667                 
#Freq Use Parent Income
Q25_demo <- Q8 %>% select(income) %>% cbind(Q25_demo) %>% select(ID, child, freq_use, income)

Q25_demo %>% drop_na() %>%
  group_by(fct_relevel(income, "$25k - $75k", "$75k - $125k", "$125k - $175k", "$175k+", "Prefer not to answer")) %>%
  count(freq_use) %>%
  mutate(prop = n/sum(n))
#Results 
#$25k - $75k	          Monthly	              2 1.0
#$75k - $125k	          A few times a year	  2	0.25
#$75k - $125k	          Monthly	              4	0.50
#$75k - $125k	          Once a year or less	  2	0.25
#$125k - $175k	        A few times a year	  2	0.5
#$125k - $175k	        Monthly	              2	0.5
#$175k+	                A few times a year	  4	0.67
#$175k+	                Once a year or less	  2	0.33
#Prefer not to answer	  A few times a year	  2	0.5
#Prefer not to answer	  Once a year or less 	2	0.5
```

###Q28 Ingestion
```{r}
#Q28: (Ingestion) In this last year, has Child 1 ingested children's makeup and body products, either intentionally or unintentionally?
#"Yes", "No", "Do not know"

# Combine data from all children into 1 table and assess distribution overall
Q28 <- all_practice_data %>% select(ID, X1_Q28, X2_Q28, X3_Q28, X4_Q28, X5_Q28)
Q28 <- Q28 %>% pivot_longer(!ID, names_to = "child", values_to = "ingest")
#view(Q28)

Q28 %>% filter(!is.na(ingest)) %>% count(ingest) %>% mutate(prop = n/sum(n))

# Results
#Ingest             n   prop
#Do not know	6	0.25		
#No	          12	0.50		
#Yes	        6	0.25		

# Freq of use by child age category 
Q28_demo <- Q12 %>% select(child_age_cat) %>% cbind(Q28) %>% select(ID, child, ingest, child_age_cat)
# view(Q28_demo)

Q28_demo %>%
  drop_na() %>%
  group_by(fct_relevel(child_age_cat, "0-3", "4-6", "10-12")) %>%
  count(ingest) %>%
  mutate(prop = n/sum(n))

#Results 
#Ingest         n       %
#0-3     No	        6	1.00
#4-6     Do not know	2	0.25
#4-6     No	        4	0.50
#4-6     Yes	        2	0.25
#10-12   Do not know	4	0.40
#10-12   No	        2	0.20
#10-12   Yes	        4	0.40
```

###Q24  
```{r}
#In the last year, approximately how much does product packaging influence Child 1 's interest in children's makeup and body products?

#"A great deal", "A moderate amount", "Very little", "Not at all", "Do not know"

# Combine data from all children into 1 table and assess distribution overall
Q24 <- all_practice_data %>% select(ID, X1_Q24, X2_Q24, X3_Q24, X4_Q24, X5_Q24)
Q24 <- Q24 %>% pivot_longer(!ID, names_to = "child", values_to = "packaging")
#view(Q24)

Q24 %>% filter(!is.na(packaging)) %>% count(fct_relevel(packaging, "A great deal", "A moderate amount", "Very little", "Not at all", "Do not know")) %>% mutate(prop = n/sum(n))

# Results
#A great deal	6	0.6		
#Very little	2	0.2		
#Not at all	2	0.2		

# Packaging Influence by child age category 
Q24_demo <- Q12 %>% select(child_age_cat) %>% cbind(Q24) %>% select(ID, child, packaging, child_age_cat)
# view(Q24_demo)

Q24_demo %>%
  drop_na() %>%
  group_by(fct_relevel(child_age_cat, "0-3", "4-6", "10-12")) %>%
  count(packaging) %>%
  mutate(prop = n/sum(n))

# Results 
# Age   packaging     n prop
#0-3    Not at all	  2	1.0000000
#4-6    A great deal	2	1.0000000
#10-12  A great deal	4	0.6666667
#10-12  Very little	  2	0.3333333


# packaging influence  by child gender
Q24_demo <- Q13 %>% select(child_gender) %>% cbind(Q24_demo) %>% select(ID, child, packaging, child_age_cat, child_gender)
#view(Q24_demo)

Q24_demo %>%
  drop_na() %>%
  group_by(child_gender) %>%
  count(packaging) %>%
  mutate(prop = n/sum(n))

#Gender Infleunce  n prop
#Female	  A great deal	6	0.75	
#Female	  Not at all	  2	0.25	
#Male	    Very little	  2	1.00	
```

###Q21 
```{r}
#Q21: (Adults/kids proportion) In the last year, what proportion of total makeup and body products used by Child 1 would be considered children's products rather than adult products?

# "None (0%)", "Few (Less than 25%), "Less than Half (25-50%)", "More than Half (50-75%)", "Large Majority (75-100%)", "Do not know"

# Combine data from all children into 1 table and assess distribution overall
Q21 <- all_practice_data %>% select(ID, X1_Q21, X2_Q21, X3_Q21, X4_Q21, X5_Q21)
Q21 <- Q21 %>% pivot_longer(!ID, names_to = "child", values_to = "kid_adult")
#view(Q21)

Q21 %>% filter(!is.na(kid_adult)) %>% count(fct_relevel(kid_adult, "None (0%)", "Few (Less than 25%)", "Less than Half (25-50%)", "More than Half (50-75%)", "Large Majority (75-100%)", "Do not know")) %>% mutate(prop = n/sum(n))

# Results
#kid_adult             n   prop
#Few (Less than 25%)	    6	  0.25000000	
#Less than Half (25-50%)	2	  0.08333333	
#More than Half (50-75%)	6	  0.25000000	
#Large Majority (75-100%)	10	0.41666667

#kid_adult  by child age category 
Q21_demo <- Q12 %>% select(child_age_cat) %>% cbind(Q21) %>% select(ID, child, kid_adult, child_age_cat)
# view(Q21_demo)

Q21_demo %>%
  drop_na() %>%
  group_by(fct_relevel(child_age_cat, "0-3", "4-6", "10-12")) %>%
  count(kid_adult) %>%
  mutate(prop = n/sum(n))

# Results 
# Age   Duration                n prop
#0-3 Few (Less than 25%)	      2	0.3333333
#0-3 Large Majority (75-100%)	  4	0.6666667
#4-6 Large Majority (75-100%)	  4	0.5000000
#4-6 Less than Half (25-50%)	  2	0.2500000
#4-6 More than Half (50-75%)	  2	0.2500000
#10-12 Few (Less than 25%)	    4	0.4000000
#10-12 Large Majority (75-100%)	2	0.2000000
#10-12 More than Half (50-75%)	4	0.4000000

# Duration of use by child gender
Q21_demo <- Q13 %>% select(child_gender) %>% cbind(Q21_demo) %>% select(ID, child, kid_adult, child_age_cat, child_gender)
#view(Q21_demo)

Q21_demo %>%
  drop_na() %>%
  group_by(child_gender) %>%
  count(kid_adult) %>%
  mutate(prop = n/sum(n))

#Results
#Gender kid_adult                  n   prop
#Female	Few (Less than 25%)	      2	0.125
#Female	Large Majority (75-100%)	10	0.625
#Female	More than Half (50-75%)	  4	0.250
#Male	Few (Less than 25%)	        4	0.500
#Male	Less than Half (25-50%)	    2	0.250
#Male	More than Half (50-75%)	    2	0.250		

#Kid_adult by child race/ethnicity
Q21_demo <- Q14 %>% select(child_race_eth) %>% cbind(Q21_demo) %>% select(ID, child, kid_adult, child_age_cat, child_gender, child_race_eth)
#view(Q21_demo)

Q21_demo %>% 
  drop_na() %>% 
  group_by(child_race_eth) %>%
  count(kid_adult) %>%
  mutate(prop = n/sum(n))

#Results
#race_eth         kid_adult                   n   prop
#Native Few (Less than 25%)	            2	1.0000000
#Black, White Few (Less than 25%)     	2	0.1250000
#Black, White Large Majority (75-100%)	8	0.5000000
#Black, White More than Half (50-75%)	  6	0.3750000
#East ASian Few (Less than 25%)	        2	0.3333333
#East Asian Large Majority (75-100%)	  2	0.3333333
#East Asian Less than Half (25-50%)	    2	0.3333333


#Kid_adult Parent Income
Q21_demo <- Q8 %>% select(income) %>% cbind(Q21_demo) %>% select(ID, child, kid_adult, income)

Q21_demo %>% drop_na() %>%
  group_by(fct_relevel(income, "$25k - $75k", "$75k - $125k", "$125k - $175k", "$175k+", "Prefer not to answer")) %>%
  count(kid_adult) %>%
  mutate(prop = n/sum(n))

#Results 
#Income   Kid_adult n prop
#$25k - $75k	More than Half (50-75%)	          2	1.0
#$75k - $125k	Large Majority (75-100%)	        4	0.5
#$75k - $125k	More than Half (50-75%)	          4	0.5
#$125k - $175k	Few (Less than 25%)	            2	0.5
#$125k - $175k	Large Majority (75-100%)	      2	0.5
#$175k+	Few (Less than 25%)	                    2	0.33
#$175k+	Large Majority (75-100%)	              2	0.33
#$175k+	Less than Half (25-50%)	                2	0.33
#Prefer not to answer	Few (Less than 25%)	      2	0.5
#Prefer not to answer	Large Majority (75-100%)	2	0.5


Q21_demo <- Q7 %>% select (education) %>% cbind(Q21_demo) %>% select(ID, child, kid_adult, education)

Q21_demo %>% drop_na() %>%
  group_by(fct_relevel(education, "Less than high school", "High school / Equivalent", "Vocational/trade school", "Some college", "Completed college", "Some graduate school or more", "Prefer not to answer")) %>%
  count(kid_adult) %>%
  mutate(prop = n/sum(n))
#Results 
#Education kid_adult                    n prop
#Vocational More than Half (50-75%)	    2	1.0000000
#Some college Large Majority (75-100%)	4	1.0000000
#Completed Few (Less than 25%)	        2	0.2500000
#Completed Large Majority (75-100%)	    2	0.2500000
#Completed More than Half (50-75%)	    4	0.5000000
#Some grad Few (Less than 25%)	        2	0.3333333
#Some grad Large Majority (75-100%)	    2	0.3333333
#Some grad Less than Half (25-50%)	    2	0.3333333
```

